Fasano Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2020-12-19 journalMS/article.tex
updated KS equations

The Kolmogorov--Smirnov (KS) test is a non--parametric method for determining where a sample is consistent with a given probability distribution. While a comprehensive discussion pertaining the intracies of the 1-D KS test can be found elsewhere~\citep{Stephens1992}, we will present a brief overview as motivation for the basis and intuition of the 2-D KS test.

@@

\begin{equation} \label{eq:1}
Q_{KS}(\lambda) = 2 \sum_{j=1}^{\infty} -1^{j-1}e^{-2j^2\lambda^2}
\end{equation}

@@

\begin{equation} \label{eq:2}
Prob(D > observed) = Q_{KS} ( D\sqrt{N})
\end{equation}

@@

\textbf{In the 2-Sample case}, the $p$-value probability of a given D-stat is defined by
\begin{equation} \label{eq:3}
Prob(D > observed) = Q_{KS} ( D\sqrt{\frac{n_1n_2}{n_1+n_2}})
\end{equation}

@@

\begin{equation} \label{eq:4}
Prob(D > observed) = Q_{KS} ( \frac{D\sqrt{N}}{1+\sqrt{1-r^2}(0.25-0.75/\sqrt{N})})
\end{equation}

>>>>

The Kolmogorov--Smirnov (KS) test is a non--parametric method for determining where a sample is consistent with a given probability distribution. While a comprehensive discussion pertaining the intracies of the 1-D KS test can be found elsewhere~\citep{Stephens1992a}, we will present a brief overview as motivation for the basis and intuition of the 2-D KS test.

@@

\begin{equation} \label{eq:1}
\Phi(\lambda) = 2 \sum_{k=1}^{\infty} -1^{k-1}e^{-2k^2\lambda^2}
\end{equation}

@@

\begin{equation} \label{eq:2}
Prob(D > observed) = \Phi ( D\sqrt{N})
\end{equation}

@@

\textbf{In the 2-Sample case}, the $p$-value probability of a given D-stat is defined by
\begin{equation} \label{eq:3}
Prob(D > observed) = \Phi ( D\sqrt{\frac{n_1n_2}{n_1+n_2}})
\end{equation}

@@

\begin{equation} \label{eq:4}
Prob(D > observed) = \Phi ( \frac{D\sqrt{N}}{1+\sqrt{1-r^2}(0.25-0.75/\sqrt{N})})
\end{equation}
